Work Fragmentation in Developer Interaction Data

### 2016-01-26 paper_2.tex
More motivation about time series and edit ratio

Multivariate time series is a useful way of representing temporal data because they allow us to apply clustering techniques and find recurrent patterns. Additionally, the partition of the data into sessions do not alter the results since we are interested in the values by minute, so having longer sessions do not necessarily increase the number of events per minute.

\RR{motivate more the time series stuff}

@@

\RR{motivate more edit ratio, and add here the correlation analysis}

>>>>

Creating time series is a useful way of representing temporal data because they allow us to apply clustering techniques and find recurrent patterns; in our case every minute of the time series contains different observation, which is the reason why we created multivariate time series. This way we can model a session as a MTS, where every minute contains the quantification of edition and selection events. The partition of the data into sessions do not alter the results since we are interested in the values by minute, so having longer sessions do not necessarily increase the number of events per minute.

%\RR{motivate more the time series stuff}

@@

An important reason to consider the edit ratio is that having an interruption requires doing activities that might increase the execution of selection events, reducing the edit events. For example reading the code, navigating around files and starting a debugging sessions are activities heavily loaded of selections events and are common activities after an interruption, according to observational studies. The edit ratio can tell us when there is a reduction of edit events due to (mainly) selection events.

%\RR{motivate more edit ratio, and add here the correlation analysis}
